Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

\item(i) For any level $l \geq 2$, fix the last group index to be $v$, and consider the set of  groups $\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}). The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
\item(ii) For each set of groups in level $l-1$, agents in level $l$ see
the history of agents in one of these groups. Therefore, for each arm
$a$, we just need one set of groups in level $l-1$ to get ``lucky''
and then all agents in level $l$ will see enough pulls of arm $a$.
\end{description}
\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}

>>>>

\item(i) For any level $l \geq 2$, fix the last group index to be $v$,
  and consider the set of groups
  $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
  and $G_{l-1,2,1}$ circled in the Figure
  \ref{fig:llevel-connecting}). The agents in this set of groups
  observe the same sub-history. They get ``lucky'' for some arm at the
  same time.
\item(ii) For each set of groups in level $l-1$, agents in level $l$ see
the history of agents in one of these groups. Therefore, for each arm
$a$, we just need one set of groups in level $l-1$ to get ``lucky''
and then all agents in level $l$ will see enough pulls of arm $a$.
\end{description}
\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}
